Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-17 Chapter-5/5-SamplesPreparation.tex
s

\chapter{Samples Preparation}\label{ch:samples}

\section{LArIAT Data}
\section{LArIAT Monte Carlo}
\subsection{G4Beamline}\label{beamlineComposition}
\subsection{Data Driven MC}\label{sec:DDMC}

\section{Energy Calibration}
\section{Tracking Studies}
In this section, we describe three studies. The first is a justification of the selection criteria for the beamline handshake with the TPC information.  We perform this study to boost  the correct identification of the particles in the TPC associated with the beamline information, while maintaining sufficient statistics for the cross section measurement. 
The second study is an optimization of the tracking algorithm, with the scope of maximizing the identification of the hadronic interaction point inside the TPC. These two studies are related, since the optimization of the tracking is performed on TPC tracks which have been matched to the wire chamber track; in turn, the tracking algorithm for TPC tracks determine the number of reconstructed tracks in each event used to try the matching with the wire chamber track. Starting with a sensible tracking reconstruction, we perform the WC2TPC matching optimization first, then the tracking optimization. The WC2TPC match purity and efficiency  are then calculated again with the optimized tracking.

@@

>>>>

\chapter{Samples Preparation}\label{ch:samples}
This chapter describes the data and Monte Carlo samples used for the cross section analyses, % as well as the work necessary to prepare the samples in a usable state for the physics analyses.
\section{LArIAT Data}
\section{LArIAT Monte Carlo}
\subsection{G4Beamline}\label{beamlineComposition}
\subsection{Data Driven MC}\label{sec:DDMC}

\section{Energy Calibration}\label{ch:EnCalibration}
\section{Tracking Studies}
In this section, we describe three studies. The first is a justification of the selection criteria for the beamline handshake with the TPC information.  We perform this study to boost  the correct identification of the particles in the TPC associated with the beamline information, while maintaining sufficient statistics for the cross section measurement. 
The second study is an optimization of the tracking algorithm, with the scope of maximizing the identification of the hadronic interaction point inside the TPC. These two studies are related, since the optimization of the tracking is performed on TPC tracks which have been matched to the wire chamber track; in turn, the tracking algorithm for TPC tracks determine the number of reconstructed tracks in each event used to try the matching with the wire chamber track. Starting with a sensible tracking reconstruction, we perform the WC2TPC matching optimization first, then the tracking optimization. The WC2TPC match purity and efficiency  are then calculated again with the optimized tracking.

@@

\subsection{Estimate of $E_{loss}$ before the TPC}
The beamline particles travel a path from when their momentum is measured by the beamline detector, until they are tracked inside the TPC. In the current LArIAT geometry, a particle leaving the fourth wire chamber will encounter the materials listed in Table \ref{tab:budget} before being registered again. The energy lost by the particle in this non instrumented material modifies the particle's kinetic energy and directly affects the cross section measurement, as shown in equation \ref{eq:enFF}.

\begin{table}[h!]
\centering
\begin{tabular}{|l|l|l|}
\hline
Material  & density {[}g/cm$^3${]} & width {[}cm{]}    \\ \hline
Fiberglass laminate (G10)      & 1.7                             & 1.28                              \\
Liquid Argon                           & 1.4                             & 3.72                             \\
Stainless Steel                        & 7.7                            & 0.23                             \\
Titanium                                  & 4.5                            & 0.04                             \\ 
Air                                            &  1.2 $\cdot10^{-3}$  & 89.43                              \\
Plastic Scintillator                    & 1.03                          & 5.30                              \\ \hline
\end{tabular}
\caption{LArIAT material budget from WC4 to the TPC Front Face.}
\label{tab:budget}
\end{table}

We estimate the uncertainty on the energy loss between the beamline momentum measurement and the TPC, $E_{loss}$, using the DDMC pion sample. We shoot pions from WC4 with the same momentum distribution as in the beamline data and plot the true $E_{loss}$ for that sample. The distribution for $E_{loss}$ for the pion sample is shown in Figure \ref{fig:Eloss}. We estimate the energy loss for pions to be $E_{loss} = 37 \pm 7 $~MeV where we use the average energy lost as the central value and the standard deviation of the distribution as the uncertainty.

\begin{figure}[hpbt]
\centering
\includegraphics[scale=0.4]{Chapter-5/Images/cELossPions.png}
\caption{Energy loss by simulated negative pions downstream from WC4 and upstream from the TPC.}
\label{fig:Eloss}
\end{figure}
